We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-08 paper/paper.tex
refs

Some studies have focused on the study of individual dark matter halos
that could host galaxies like the MW or M31, while some other studies
have tried to simulate the formation of galaxy pairs resembling both
the MW and M31.
The transition from studying individual halos to pairs has been
motivated by studies that show how the LG location in the cosmic web
plays a role in distingushing the the MW and M31 halos from the
average $\sim 10^{12}$ \Msun DM halo.

the cosmic web should play a determinant role in building up planar
satellite distributions through preferential alignments and accretions
histories of galaxies.

Studies of the Local Group in an explicit cosmological context have
also renewed the interest on performing constrained simulations that
could reproduce the observed large scale structure of the Universe,
This has also motivated the study of the two dominant galaxies in the 
Local Group as a pair in a cosmological context finding that the LG
itself has relatively uncommon kinematic configuration in the context
of LCDM and a strong preference to lie along filaments.

>>>>

Some studies have focused on the study of individual dark matter halos
that could host galaxies like the MW or M31, while some other studies
have tried to simulate the formation of galaxy pairs resembling both
the MW and M31.
The transition from individual halos to pairs has been
motivated by studies that show how the LG location in the cosmic web
plays a role in distingushing the the MW and M31 halos from the
average $\sim 10^{12}$ \Msun\ DM halo \citep{2011MNRAS.417.1434F}
Studies of the LG as a pair of isolated DM halos have also found that
the LG itself has relatively atypical kinematicsin the context
of LCDM and a strong preference to lie along filaments \citep{ForeroRomero2013}.
Putting together these pieces, the cosmic web should therefore play a
determinant role in building up planar satellite distributions through
preferential alignments and accretions histories of galaxies
\citep{2014MNRAS.443.1090F}.
